### 2023-02-07 article.tex
Improve

The practice of using a code hosting websote has increased,
with the abstracts from articles in the academic journal
'Bioinformatics' referring to such a hosted website
has increased tenfold, going from below 5 percent in 2009 
to around 50 percent in 2017 \cite{russell2018large}.

@@

Hosted code commonly has a commit history. For example, GitHub
uses a version control system called \verb|git| (hence its name).
In practice, this means that when a change is made to the code,
a new version is created. In the case that the change was harmful,
one can go back to an earlier version and continue again from there.
It is a general recommendation to put version control
on all human-produced data \cite{wilson2014best}.

@@

% \paragraph{A reader can contact the author}

A feature that gets too few attention is that code hosts
allow users to post bug reports and/or ask questions.
This allows other researchers to assess the health
of the code.
A healthy project has few open bug reports
and these bug reports should be closed within reasonable time.
When bug reports start to accumulate, this
signals either that the code contained many bugs or that
the developers lost interest in maintaining that code.
The amount of bug reports is useful metadata, 
especially when deciding to use (and depend) on a piece of software.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Making code FAIR data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% Reviewer 1: this section starts with a sentence that appears to undercut the whole theme of this chapter!
Code may or may not be paradata, depending on how the definition
is interpreted.
Here we repeat the definition of 'paradata' and discuss 
its constituents.
This paper defined paradata as 'data about the collecting of the data'.
This implies that (1) code must be seen as data.
This paper argues, that code is data in the form of text spread
over one or more files with useful measurable properties.
(2) downloading raw data and doing calculations must be seen as collecting.
This paper argues that downloading raw datas and doing calculations, 
such as a T-test,
does describe how the bits and pieces of an end result are collected.
(3) the results of an experiment must be seen as data.
This paper argues that an experimental results is data, 
as it can be measured and can be used as the raw data of a next experiment.

@@

Code has additional useful information, similar to confidence intervals,
that allow a reader to gauge how much one trusts the results.
The more of the best practices are followed, 
the more trustworthy are the results.
The most important best practices discussed in this paper are
automatic testing, having a high code coverage and code
of low (cyclomatic) complexity.
In academia, to uncover the truth, code correctness is essential,
similar to cell biologists working sterile to not contaminate their
cell cultures.
These best practices are vital for a computational biologist.

>>>>

The practice of using a code hosting website has increased,
with the abstracts from articles in the academic journal
'Bioinformatics' referring to such a hosted website
has increased tenfold, going from below 5 percent in 2009 
to around 50 percent in 2017 \cite{russell2018large}.

@@

Hosted code commonly has a commit history. For example, GitHub
uses a version control system called \verb|git| (hence its name).
In practice, this means that when a change is made to the code,
a new version is created. In the case that the change was harmful,
one can go back to an earlier version and continue again from there.
It is a general recommendation to put version control
on all human-produced data \cite{wilson2014best},
as well as openly working on the code from the start \cite{jimenez2017four}.

@@

\paragraph{Adding a license}

Code hosting websites such as GitHub help developers to follow
best practices. One of these is to add a software license \cite{jimenez2017four},
so that it is clear that the software can be reused.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Preserving code}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@
